### 2022-04-23 experiments.tex
Reformat the paper

A target pitch extraction examples selected from the test set is shown in Figure~\ref{fig:pitch_1}.
\begin{figure}[t]
    \stackunder[5pt]{\includegraphics[width=\linewidth]{img/pitch.eps}}{(a)}
    \stackunder[5pt]{\includegraphics[width=\linewidth]{img/spec_mix.eps}}{(b)}
    \stackunder[5pt]{\includegraphics[width=\linewidth]{img/spec_target.eps}}{(c)}

>>>>

A target pitch extraction examples selected from the test set is shown in Figure~\ref{fig:pitch_1}.
\begin{figure}[!htbp]
    \centering
    \stackunder[5pt]{\includegraphics[width=0.45\linewidth]{img/pitch.eps}}{(a)}
    \stackunder[5pt]{\includegraphics[width=0.45\linewidth]{img/spec_mix.eps}}{(b)}
    \stackunder[5pt]{\includegraphics[width=0.45\linewidth]{img/spec_target.eps}}{(c)}
